\thesistitle

### 2019-06-11 sections/research.tex
Nicer looking example

\subsection{Type 2 clones}
Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in listing \ref{lst:type2clone} are type 2 clones of each other.

\begin{lstlisting}[caption={Methods that are type 2 clones but functionally completely different.},label={lst:type2clone},language=Java]
public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
	return listOfCircles.stream().allMatch(Shape::isRed);
}

public Apple getEatableAppleFromBasket(FruitBasket<Apple> appleBasket){
	return appleBasket.getFruitContainer().getAppleByCriterium(Fruit::hasNotYetBeenEaten);
}
\end{lstlisting}

@@

\subsubsection{Variables}

@@

Integrated in JavaParser is a library named SymbolSolver. This library allows for the resolution of symbols using JavaParser. For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called `symbols`). This is very useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.

>>>>

\subsection{Type 2 clones}
Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type2}
  \caption{Example of a type 2 clone.}
  \label{fig:type2}
\end{figure}

@@

\subsubsection{Variables}
In typed programming languages, each variable declaration should declare a name and a type. When we reference a variable, we only use its name. If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal. As an example, see the code in listing \ref{lst:type2variables}.

\begin{lstlisting}[caption={Variables with different types but the same name.},label={lst:type2variables},language=Java]
public String appendFive(String x){
	return x + 5;
}

public int addFive(int x){
	return x + 5;
}
\end{lstlisting}

The body of both methods in listing \ref{lst:type2variables} is equal. However, their functionality is not.

@@

Integrated in JavaParser is a library named SymbolSolver. This library allows for the resolution of symbols using JavaParser. For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols''). This is very useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
